Irt plot extra

### 2023-11-07 manuscript_SciRep.Rmd
Comments addressed and typo corrected-MASj

keywords          : "light exposure, light-related behaviours, non-visual effects of light, psychometrics"
wordcount         : "6314"

@@

#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr, paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,reshape, ggsci,ggtext)
webshot::install_phantomjs()
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))
install.packages("latticeExtra")
install.packages("correlation")
install.packages("ggtext")
#if you don't have LaTeX installed run the following lines
#install.packages("tinytex")
#tinytex::install_tinytex()
```

@@

Lastly, this study is the lack of convergent validity evidence. LEBA being the first of its kind, lacks golden standard against which its convergent validity evidence  could be established. However, a recent study [@Siraji.2023] demonstrates the predictive validity of LEBA by successfully relating LEBA behaviour factors to chronotype, mood, sleep quality, and memory and concentration difficulties. The results of their study confirmed the very essence of LEBA-behaviour could led to different light exposure experiences that differentially influence health, wellness and performance.

>>>>

keywords          : "light exposure, light-related behaviours, non-visual effects of light, psychometrics"
wordcount         : "5767"

@@

#You need to run this chunk 1X in your system 
install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr, paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,reshape, ggsci,ggtext)
webshot::install_phantomjs()
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))
install.packages("latticeExtra")
install.packages("correlation")
install.packages("ggtext")
#if you don't have LaTeX installed run the following lines
install.packages("tinytex")
tinytex::install_tinytex()
```

@@

Lastly, this study lacks convergent validity evidence. LEBA being the first of its kind, lacks golden standard against which its convergent validity evidence  could be established. However, a recent study [@Siraji.2023] demonstrates the predictive validity of LEBA by successfully relating LEBA behaviour factors to chronotype, mood, sleep quality, and memory and concentration difficulties. The results of their study confirmed the very essence of LEBA-behaviour could led to different light exposure experiences that differentially influence health, wellness and performance.
